### 2011-05-06 paper/paper.tex
More images!

\begin{figure}
\subfloat[Standard]{\epsfig{file=images/gaussian_5000_cube10_cold,width=8cm}}
\subfloat[Adaptive]{\epsfig{file=images/gaussian_adaptive_5000_cube10_cold,width=8cm}}
\caption{5000 iteration Gaussian walking methods on the 10 dimensional cube with a bad start}
\end{figure}

@@

These results indicate that, in practice, the hit-and-run method is better than the Metropolis methods, even when taking into account its slower transition step. Among the Metropolis methods, the Gaussian-walking method is a slight improvement over the ball-walking method, and the adaptive methods always help in cases where are starting point is near a corner.

>>>>

\begin{figure}
\centering
\subfloat[Standard]{\epsfig{file=images/gaussian_5000_cube10_cold,width=8cm}}
\subfloat[Adaptive]{\epsfig{file=images/gaussian_adaptive_5000_cube10_cold,width=8cm}}
\caption{5000 iteration Gaussian walking methods on the 10 dimensional cube with a bad start}
\end{figure}

\begin{figure}
\centering
\subfloat[Standard]{\epsfig{file=images/gaussian_2000_cube10_cold,width=8cm}}
\subfloat[Adaptive]{\epsfig{file=images/gaussian_adaptive_2000_cube10_cold,width=8cm}}
\caption{2000 iteration Gaussian walking methods on the 10 dimensional cube with a bad start}
\end{figure}

\begin{figure}
\centering
\subfloat[Standard Ball-Walking]{\epsfig{file=images/ballwalk_5000_cube100_warm,width=5.4cm}}
\subfloat[Adaptive Ball-Walking]{\epsfig{file=images/ballwalk_adaptive_5000_cube100_warm,width=5.4cm}}
\subfloat[Standard Gaussian-Walking]{\epsfig{file=images/gaussian_5000_cube100_warm,width=5.4cm}}
\caption{5000 iteration Metropolis methods on the 100 dimensional cube with a good start}
\end{figure}

\begin{figure}
\centering
\subfloat[10 dimensional cube, bad start]{\epsfig{file=images/hitandrun_1200_cube10_cold,width=8cm}}
\subfloat[100 dimensional cube, good start]{\epsfig{file=images/hitandrun_1200_cube100_warm,width=8cm}}
\caption{1200 iteration hit-and-run method on the 10 dimensional and 100 dimensional cubes}
\end{figure}

\begin{figure}
\centering
\subfloat[5000 Iteration Standard Ball-Walking]{\epsfig{file=images/ballwalk_5000_sphere100_cold,width=8cm}}
\subfloat[5000 Iteration Adaptive Ball-Walking]{\epsfig{file=images/ballwalk_adaptive_5000_sphere100_cold,width=8cm}}

\subfloat[5000 Iteration Standard Gaussian-Walking]{\epsfig{file=images/gaussian_adaptive_5000_sphere100_cold,width=8cm}}
\subfloat[5000 Iteration Adaptive Gaussian-Walking]{\epsfig{file=images/gaussian_5000_sphere100_cold,width=8cm}}

\subfloat[1200 Iteration Hit and Run]{\epsfig{file=images/hitandrun_1200_sphere100_cold,width=8cm}}
\caption{Sampling methods on the 100 dimensional sphere with a bad start}
\end{figure}

@@

These results indicate that, in practice, the hit-and-run method is better than the Metropolis methods, even when taking into account its slower transition step. Among the Metropolis methods, the Gaussian-walking method is a slight improvement over the ball-walking method, and the adaptive methods usually help in cases where are starting point is near a corner.
